---
title: 'CTT analysis for test: `r thistest$test_name`'
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
  word_document: default
date: "Generated `r date()`"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, results = "asis")

```


**Number of items:** `r x$number_items`

**Number of examinees:** `r x$number_examinees`


## Total score information

```{r totalscores}
test_info_out(x)

```


## Reliability

```{r reliability}
knitr::kable(getReliability(x), digits = 2)

```

*Note:* Although Coefficient Alpha is a popular measure of reliability, it relies on model assumptions that are rarely met practice which leads to a biased estimate of reliability (see Dunn, T. J., Baguley, T., & Brunsden, V., 2014 for a summary if the issues with Alpha). Therefore, we suggest using one of the other reliability measures which rely on assumptions much more commonly met in practice.

## Item overview

```{r item_overview}
overview = getItemOverview(x)

knitr::kable(overview, digits = 2)

plotItemOverview(overview)
```


## Item details

```{r distractor_report}
distractor_report(x)
```


